\section{Simulation}
\label{sec:SimSection}

We now compare the performance of the above formulation of quantile $e$-values in a simulation setup. For this, consider the model in (\ref{eqn:LMMeqn}) with no environmental covariates. We consider familes with MZ twins and first generate the covariate matrices $\bfG_i$. We take a total of $p_g = 50$ SNPs, and to simulate correlation among SNPs in the genome generate them in correlated blocks of 6, 4 ,6, 4 and 30. We set the correlation between two SNPs inside a block at 0.7, and consider the blocks to be uncorrelated. For each parent we generate two independent vectors of length 50 with the above correlation structure, and entries within each block being 0 or 1 following Bernoulli distributions with probabilities 0.2, 0.4, 0.4, 0.25 and 0.25 (Minor Allele Frequency or MAF) for SNPs in the 5 blocks, respectively. The genotype of a person is then determined by taking the sum of these two vectors: thus entries in $\bfG_i$ can take the values 0, 1 or 2. Finally we set the common genotype of the twins by randomly choosing one allele vector from each of the parents and taking their sum.

We repeat the above process for $m=250$ families. In GWAS there are generally a small number of causal SNPs, each explaining small proportions of the overall variability in response variable. To reflect this in our simulation setup, we assume that the first entries in each of the first four blocks above are causal, and each of them explains $h/(\sigma_a^2+\sigma_c^2+\sigma_e^2) \%$ of the overall variability. The term $h$ is known as the \textit{heritability} of the corresponding SNP (and can of course vary across SNPs). The value of the non-zero coefficient in $k$-th group: $k = 1, ..., 4$, say $\beta_k$ is calculated using the formula:
%
\begin{align}
\beta_k = \sqrt{ \frac{h}{(\sigma_a^2+\sigma_c^2+\sigma_e^2). 2 \text{MAF}_k (1 - \text{MAF}_k) }}
\end{align}
%
We fix the following values for the error variance components: $\sigma_a^2 = 4, \sigma_c^2 = 1, \sigma_e^2 = 1$, and generate pedigree-wise response vectors $\bfy_1, \ldots, \bfy_{250}$ using the above setup. To consider different SNP effect sizes, we repeat the above setup for $h \in \{10, 5, 2, 1, 0 \}$, generating 1000 datasets for each value of $h$.

\subsection{Methods and metrics}
For this simulated data, we compare our $e$-value based approach with two other methods:

\paragraph{(1) Model selection on linear model:} Here we ignore the dependency structure within families by training linear models on the simulated data and selecting SNPs with non-zero effects by backward deletion using a modification of the BIC called mBIC2. This has been showed to give better results than single-marker analysis in GWAS for unrelated individuals \citep{FrommeletEtal12} and provides approximate False Discovery Rate (FDR) control at level 0.05 \citep{BogdanEtal11}.

\paragraph{(2) Single-marker mixed model:} We train single-SNP versions of (\ref{eqn:LMMeqn}) using a fast approximation of the Generalized Least Squares procedure (named Rapid Feasible Generalized Least Squares or RFGLS: \cite{LiEtal11}), obtain marginal $p$-values from corresponding $t$-tests and use the Benjamini-Hochberg (BH) procedure to select significant SNPs at FDR = $0.05$.

\vspace{1em}\noindent We compute the $e$-values by setting projection depth \citep{zuo03} as the evaluation function. With the $e$-value being the $q$-th quantile of the evaluation map distribution, we set the detection threshold value at the $t$-th multiple of $q$ for some $0 < t < 1$. This means all indices $j$ such that $q$-th quantile of the bootstrap approximation of $\BE_{-j,n} $ is less than the $tq$-th quantile of the bootstrap approximation of $\BE_{* n}$ will get selected as the set of active predictors. We repeat the $e$-value procedure for different values of the bootstrap standard deviation $s \in \{ 0.3, 0.15, \ldots, 0.95, 2 \}$. Consequently, we take as the final estimated set of SNPs the SNP set $\hat \cS (s)$ that minimizes fixed effect prediction error (PE) on an independently generated test dataset $\{ (\bfy_{test,i}, \bfG_{test,i}), i = 1, \ldots, 250 \}$ from the same setup above:
%
\begin{align*}
& \text{PE} (s | q,t)  = \sum_{i=1}^{250} \sum_{j=1}^4 \left( y_{test,ij} - \bfg_{test,ij}^T \hat \bfbeta_{\hat \cS (s)} \right)^2; \\
& \hat \cS_0 (q,t) = \argmin_s \text{PE} (s | q,t)
\end{align*}

The metrics to evaluate each method we implement are:

\begin{enumerate}
\item True Positive (TP): proportion of causal SNPs detected;

\item True Negative (TN): proportion of non-causal SNPs undetected;

\item Relaxed True Positive (TPR): proportion of detecting any SNP in each of the 4 blocks with causal SNPs, i.e. for the selected index set $\hat \cS_0 (q,t)$,
%
$$
\text{TPR} ( \hat \cS_0 (q,t) ) = \frac{1}{4} \sum_{i=1}^4 \BI ( \text{Block } i \cap \hat \cS_0 (q,t) \neq \emptyset )
$$
%

\item Relaxed True Negative (TNR): proportion of SNPs in block 5 undetected.
\end{enumerate}

\noindent We consider the third and fourth metrics to cover situations in which the causal SNP is not detected itself, but highly correlated SNPs with the causal SNP are. This is common in GWAS. Finally, we average all the above proportions over 1000 replications, and repeat the process for $ q \in \{ 0.9, 0.5, 0.2, 0.1 \}; t \in \{ 0.8, 0.7, 0.6, 0.5 \}$.

%Although the first two heritability values are larger compared to a typical GWAS setup, we use this setup to demonstrate limitations of the existing methodology even in a vastly simplified setting.

\subsection{Results}
% latex table generated in R 3.3.2 by xtable 1.8-2 package
% Sun Apr 16 18:24:09 2017
% latex table generated in R 3.3.2 by xtable 1.8-2 package
% Sun Apr 16 18:24:48 2017
\begin{table}
\begin{footnotesize}
\centering
    \begin{tabular}{c|c|c|c|cccc}
    \hline
     6x   & mBIC2       & RFGLS  & \multicolumn{5}{|c}{quantile $e$-values}    \\\cline{4-8}
    Heritability    &           & +BH		 & $q$    & $t=0.8$     & $t=0.7$     & $t=0.6$     & $t=0.5$     \\ \hline
    ~    & ~         & ~         & 0.9      & 0.95/0.97 & 0.95/0.97 & 0.95/0.98 & 0.94/0.98 \\
    $h=10$ & 0.79/0.99 & 0.95/0.92 & 0.5      & 0.96/0.97 & 0.96/0.98 & 0.95/0.98 & 0.94/0.98 \\
    ~    & ~         & ~         & 0.2      & 0.96/0.94 & 0.96/0.97 & 0.95/0.97 & 0.95/0.98 \\\hline
    ~    & ~         & ~         & 0.9      & 0.72/0.95 & 0.7/0.96  & 0.69/0.96 & 0.66/0.97 \\
    $h=5$  & 0.41/0.99 & 0.62/0.97 & 0.5      & 0.78/0.94 & 0.75/0.94 & 0.72/0.95 & 0.71/0.96 \\
    ~    & ~         & ~         & 0.2      & 0.83/0.91 & 0.78/0.94 & 0.75/0.95 & 0.73/0.95 \\\hline
    ~    & ~         & ~         & 0.9      & 0.26/0.97 & 0.24/0.97 & 0.23/0.98 & 0.21/0.98 \\
    $h=2$  & 0.11/0.99 & 0.14/0.99 & 0.5      & 0.34/0.95 & 0.28/0.96 & 0.27/0.97 & 0.26/0.97 \\
    ~    & ~         & ~         & 0.2      & 0.46/0.91 & 0.34/0.95 & 0.3/0.96  & 0.27/0.96 \\\hline
    ~    & ~         & ~         & 0.9      & 0.12/0.98 & 0.1/0.98  & 0.09/0.99 & 0.08/0.99 \\
    $h=1$  & 0.05/0.99 & 0.04/0.99    & 0.5      & 0.16/0.96 & 0.13/0.97 & 0.12/0.97 & 0.11/0.98 \\
    ~    & ~         & ~         & 0.2      & 0.25/0.93 & 0.16/0.96 & 0.13/0.97 & 0.13/0.97 \\\hline
    ~    & ~         & ~         & 0.9      & --/0.99 & --/0.99 & --/0.99 & --/0.99    \\
    $h=0$  & --/0.99 & --/0.99       & 0.5      & --/0.98 & --/0.98 & --/0.99 & --/0.99 \\
    ~    & ~         & ~         & 0.2      & --/0.94 & --/0.98 & --/0.98 & --/0.99 \\\hline
    \end{tabular}
    \caption{Average True Positive (TP) and True Negative (TN) proportions over 1000 replications for all three methods}
    \label{table:SNPSimTable0}
\end{footnotesize}
\end{table}

%% latex table generated in R 3.3.2 by xtable 1.8-2 package
%% Sun Apr 16 18:24:09 2017
%% latex table generated in R 3.3.2 by xtable 1.8-2 package
%% Sun Apr 16 18:24:48 2017
%\begin{table}
%\begin{footnotesize}
%\centering
%    \begin{tabular}{c|c|c|c|cccc}
%    \hline
%    6x    & mBIC2       & RFGLS  & \multicolumn{5}{|c}{quantile $e$-values}    \\\cline{4-8}
%    Heritability    &           & +BH		 & $q$    & $t=0.8$     & $t=0.7$     & $t=0.6$     & $t=0.5$     \\ \hline
%     ~    & 0.27/0.98 & 0.96/0.99 & 0.9      & 0.95/0.97 & 0.95/0.97 & 0.94/0.97 & 0.94/0.98 \\
%    ~    & ~         & ~         & 0.5      & 0.98/0.96 & 0.97/0.97 & 0.96/0.97 & 0.96/0.97 \\
%    h=10 & ~         & ~         & 0.2      & 0.99/0.9  & 0.97/0.96 & 0.97/0.97 & 0.96/0.97 \\
%    ~    & ~         & ~         & 0.1      & 0.99/0.83 & 0.98/0.93 & 0.97/0.96 & 0.96/0.97 \\
%    ~    & ~         & ~         & 0.05     & 0.99/0.74 & 0.98/0.88 & 0.97/0.94 & 0.97/0.96 \\ \hline
%    ~    & 0.16/0.98 & 0.63/0.99 & 0.9      & 0.74/0.95 & 0.73/0.95 & 0.71/0.96 & 0.69/0.97 \\
%    ~    & ~         & ~         & 0.5      & 0.83/0.93 & 0.78/0.94 & 0.76/0.95 & 0.75/0.95 \\
%    h=5  & ~         & ~         & 0.2      & 0.9/0.87  & 0.83/0.93 & 0.79/0.94 & 0.76/0.95 \\
%    ~    & ~         & ~         & 0.1      & 0.93/0.79 & 0.86/0.9  & 0.81/0.93 & 0.78/0.94 \\
%    ~    & ~         & ~         & 0.05     & 0.95/0.72 & 0.88/0.86 & 0.83/0.91 & 0.79/0.93 \\ \hline
%    ~    & 0.09/0.98 & 0.16/1    & 0.9      & 0.32/0.96 & 0.29/0.97 & 0.27/0.97 & 0.24/0.98 \\
%    ~    & ~         & ~         & 0.5      & 0.45/0.94 & 0.34/0.96 & 0.32/0.96 & 0.3/0.97  \\
%    h=2  & ~         & ~         & 0.2      & 0.66/0.86 & 0.47/0.93 & 0.38/0.95 & 0.33/0.96 \\
%    ~    & ~         & ~         & 0.1      & 0.77/0.79 & 0.57/0.9  & 0.43/0.94 & 0.37/0.95 \\
%    ~    & ~         & ~         & 0.05     & 0.82/0.71 & 0.64/0.85 & 0.5/0.92  & 0.41/0.94 \\ \hline
%    ~    & 0.07/0.98 & 0.05/1    & 0.9      & 0.16/0.97 & 0.14/0.98 & 0.13/0.98 & 0.11/0.99 \\
%    ~    & ~         & ~         & 0.5      & 0.26/0.95 & 0.18/0.97 & 0.17/0.97 & 0.15/0.98 \\
%    h=1  & ~         & ~         & 0.2      & 0.5/0.88  & 0.28/0.94 & 0.2/0.96  & 0.17/0.97 \\
%    ~    & ~         & ~         & 0.1      & 0.65/0.79 & 0.4/0.91  & 0.26/0.95 & 0.2/0.97  \\
%    ~    & ~         & ~         & 0.05     & 0.73/0.71 & 0.51/0.86 & 0.35/0.92 & 0.24/0.95 \\ \hline
%    ~    & 0.05/0.98 & 0.01/1    & 0.9      & 0.04/0.98 & 0.04/0.99 & 0.03/0.99 & 0.03/0.99 \\
%    ~    & ~         & ~         & 0.5      & 0.1/0.97  & 0.05/0.98 & 0.04/0.98 & 0.04/0.98 \\
%    h=0  & ~         & ~         & 0.2      & 0.32/0.89 & 0.1/0.96  & 0.06/0.98 & 0.05/0.98 \\
%    ~    & ~         & ~         & 0.1      & 0.5/0.82  & 0.22/0.93 & 0.1/0.97  & 0.06/0.98 \\
%    ~    & ~         & ~         & 0.05     & 0.64/0.73 & 0.37/0.87 & 0.2/0.94  & 0.09/0.97 \\ \hline
%    \end{tabular}
%    \caption{Average Relaxed True Positive (TPR) and Relaxed True Negative (TNR) proportions over 1000 replications for all three methods}
%    \label{table:SNPSimTable1}
%\end{footnotesize}
%\end{table}
\begin{table}
\begin{footnotesize}
\centering
    \begin{tabular}{c|c|c|c|cccc}
    \hline
    6x    & mBIC2       & RFGLS  & \multicolumn{5}{|c}{quantile $e$-values}    \\\cline{4-8}
    Heritability    &           & +BH		 & $q$    & $t=0.8$     & $t=0.7$     & $t=0.6$     & $t=0.5$     \\ \hline
    ~    & ~         & ~         & 0.9      & 0.96/0.97 & 0.96/0.97 & 0.95/0.98 & 0.94/0.98 \\
    $h=10$ & 0.84/0.99 & 0.96/0.99 & 0.5      & 0.96/0.97 & 0.96/0.97 & 0.95/0.98 & 0.95/0.98 \\
    ~    & ~         & ~         & 0.2      & 0.97/0.95 & 0.96/0.97 & 0.96/0.97 & 0.95/0.98 \\\hline
    ~    & ~         & ~         & 0.9      & 0.73/0.95 & 0.71/0.95 & 0.7/0.96  & 0.67/0.97 \\
    $h=5$  & 0.48/0.99 & 0.64/0.99 & 0.5      & 0.79/0.93 & 0.76/0.94 & 0.73/0.95 & 0.72/0.95 \\
    ~    & ~         & ~         & 0.2      & 0.85/0.91 & 0.79/0.93 & 0.76/0.94 & 0.74/0.95 \\\hline
    ~    & ~         & ~         & 0.9      & 0.29/0.96 & 0.27/0.97 & 0.25/0.98 & 0.23/0.98 \\
    $h=2$  & 0.16/0.99 & 0.16/0.99    & 0.5      & 0.37/0.95 & 0.31/0.96 & 0.3/0.96  & 0.29/0.97 \\
    ~    & ~         & ~         & 0.2      & 0.53/0.91 & 0.38/0.95 & 0.33/0.95 & 0.3/0.96  \\\hline
    ~    & ~         & ~         & 0.9      & 0.15/0.97 & 0.13/0.98 & 0.12/0.98 & 0.1/0.99  \\
    $h=1$  & 0.08/0.99 & 0.05/0.99    & 0.5      & 0.2/0.96  & 0.17/0.97 & 0.15/0.97 & 0.13/0.98 \\
    ~    & ~         & ~         & 0.2      & 0.35/0.93 & 0.21/0.96 & 0.17/0.97 & 0.16/0.97 \\\hline
    ~    & ~         & ~         & 0.9      & --/0.97 & --/0.98 & --/0.98 & --/0.99 \\
    $h=0$  & --/0.98 & --/0.99    & 0.5      & --/0.95 & --/0.97 & --/0.97 & --/0.98 \\
    ~    & ~         & ~         & 0.2      & --/0.90 & --/0.95 & --/0.97 & --/0.97 \\\hline
    \end{tabular}
    \caption{Average Relaxed True Positive (TPR) and Relaxed True Negative (TNR) proportions over 1000 replications for all three methods}
    \label{table:SNPSimTable1}
\end{footnotesize}
\end{table}

We present the simulation results in tables \ref{table:SNPSimTable0} and \ref{table:SNPSimTable1}. Applying BIC on linear models performs poorly compared RFGLS and then correction for multiple testing on marginal LMMs for all heritability values: possibly because the linear models are trained on a smaller amount of data and ignore the variation due to shared environment in the parents.

Our proposed $e$-values work better than the two methods for detecting true signals across different values of $h$: the average TP rate going down slowly than other methods across the majority of choices for $(q,t)$. Both mBIC2 and RFGLS+BH have very high true negative detection rates, which is matched by our method for higher values of $q$. Since all reduced model distributions reside on the left of the full model distribution, we expect the variable selection process to turn more conservative at higher values of $t$.This effect is more noticeable for lower $q$. This indicates that the right tails of evaluation map distributions are more useful for this purpose. Finally for $h=0$, we report only TN or TNR values since no signals should ideally be detected: in terms of this a value of $q=0.9$ or $q=0.5$ leads to the same TN and TNR performance as RFGLS+BH for all choices of $t$. Finally, TPR performances for all methods are better than the corresponding TPTN performances. However, for mBIC2 this seems to be due to detecting SNPs in the first four blocks by chance since for $h=0$ its TNR is less than TN.

Considering that when analyzing a large number of SNPs false positives need to be minimized, setting $q=0.9, t=0.5$ is a safe choice choice for $e$-values in this simulation setup. Note here that the previous model selection algorithm using $e$-values depended on comparing the mean of the evaluation map distribution $\BE_{-j,n}$ with that of $\BE_{* n}$. Compared to that here we end up comparing a tail quantile of $\BE_{-j,n}$, and set the detection threshold at a smaller value than the same quantile of $\BE_{* n}$.